Time invariant analysis of epidemics with \pkg{EpiCompare}

### 2020-12-15 jss/EpiCompare-paper/EpiCompare-paper.Rmd
update to paper (includes comparison of a true observation to simulationed observations). I've seen a different seed give .03 instead of 0 proportion above.

```{r echo = FALSE}
devtools::load_all()
library(tidyr)
library(dplyr)
library(knitr)
library(kableExtra)
library(ggplot2)

@@

HERE BEN IS GOING TO LOOK AT THE EPIMODEL OUTPUT DIFFERENT PREDICTION BAND THINGS.

\begin{itemize}
\item thing
\end{itemize}

>>>>

```{r echo = FALSE}
devtools::load_all()
library(tidyr)
library(dplyr)
library(knitr)
library(kableExtra)
library(ggplot2)
set.seed(2)

@@

```{r echo = F}
simple_sir <- both_models %>% filter(Type == "Simple SIR") %>%
  rename(S = "X0", I = "X1", R = "X2") %>%
  select(Type, sim, t, S, I, R)

hagelloch_sir2 <- hagelloch_sir %>%
  rename(t = "time") %>%
  mutate(Type = "true observation",
         sim = 0) %>%
  select(Type, sim, t, S, I, R)
```
```{r}
# after cleaning up and combining 
all_together_df <- rbind(simple_sir,
                         hagelloch_sir2)
all_together_df[c(1:2, nrow(all_together_df) - c(1:0)),]

compression_df <- all_together_df %>% group_by(Type, sim) %>% 
  filament_compression(data_columns = c("S","I","R"), 
                       number_points = 20)
```

```{r echo = F}
# # -OR- for 2d onto the simplex (done under the hood in geom_prediction_band:
# compression_df <- all_together_df %>% 
#   as.data.frame() %>% # just to be sure...
#   get_xy_coord(xyz_col = c("S", "I", "R")) %>% # to 2d simplex space
#   group_by(Type, sim) %>%
#   filament_compression(data_columns = c("x","y"), 
#                        number_points = 20)

```{r}
dmat <- compression_df %>% 
  dist_matrix_innersq_direction(
    position = c(1:length(compression_df))[
      names(compression_df) %in% c("S","I", "R")],
    id_as_columns = T)

tdmat <- tidy_dist_mat(as.matrix(dmat[,-c(1:2)]),
                       rownames_df = ungroup(dmat[,1:2]),
                       colnames_df = ungroup(dmat[,1:2]))

simple_sir_true_obs_info <- tdmat %>% 
  compare_new_to_rest_via_distance(
    new_name_id = data.frame(Type = "true observation", sim = 0),
    distance_func = distance_psuedo_density_function, 
    sigma = "20%")

```{r echo = F}
# EpiModel simulations:
epimodel_sir <- both_models %>% filter(Type == "EpiModel SIR") %>%
  rename(S = "X0", I = "X1", R = "X2") %>%
  select(Type, sim, t, S, I, R)

hagelloch_sir2 <- hagelloch_sir %>%
  rename(t = "time") %>%
  mutate(Type = "true observation",
         sim = 0) %>%
  select(Type, sim, t, S, I, R)

all_together_df <- rbind(epimodel_sir,
                         hagelloch_sir2)

compression_df <- all_together_df %>% group_by(Type, sim) %>% 
  filament_compression(data_columns = c("S","I","R"), 
                       number_points = 20)

dmat <- compression_df %>% 
  dist_matrix_innersq_direction(
    position = c(1:length(compression_df))[
      names(compression_df) %in% c("S","I", "R")],
    id_as_columns = T)

tdmat <- tidy_dist_mat(as.matrix(dmat[,-c(1:2)]),
                       rownames_df = ungroup(dmat[,1:2]),
                       colnames_df = ungroup(dmat[,1:2]))

epimodel_sir_true_obs_info <- tdmat %>% 
  compare_new_to_rest_via_distance(
    new_name_id = data.frame(Type = "true observation", sim = 0),
    distance_func = distance_psuedo_density_function, 
    sigma = "20%") 
```

```{r hagelloch-extremeness, echo = FALSE}
simple_sir_info <- simple_sir_true_obs_info %>%
  select(-sim) %>%
  mutate(Type = "Simple SIR")
eimodel_sir_info <- epimodel_sir_true_obs_info %>%
  select(-sim) %>%
  mutate(Type = "EpiModel SIR")

rbind(simple_sir_info, eimodel_sir_info)  %>%
  kable(format = "latex", booktabs = TRUE, 
        col.names = 
          linebreak(c("Type",
                      "simulations-based estimated psuedo-density",
              "proportion of simulations with lower estimated psuedo-density"),
              align = c("l")),
        caption = paste("The extremeness of the true simulations based on",
                        "comparing psuedo-density estimates between true",
                        "vs simulated curves"), label = "hags-extreme") %>%
  kable_styling(position = "center", latex_options = "hold_position") %>%
  column_spec(2:3, width = "6cm")
```

### 2020-12-15 jss/EpiCompare-paper/EpiCompare-paper.tex
update to paper (includes comparison of a true observation to simulationed observations). I've seen a different seed give .03 instead of 0 proportion above.

HERE BEN IS GOING TO LOOK AT THE EPIMODEL OUTPUT DIFFERENT PREDICTION
BAND THINGS.

\begin{itemize}
\item thing
\end{itemize}

>>>>

\begin{CodeChunk}
\begin{CodeInput}
R> # after cleaning up and combining 
R> all_together_df <- rbind(simple_sir,
+                          hagelloch_sir2)
R> all_together_df[c(1:2, nrow(all_together_df) - c(1:0)),]
\end{CodeInput}
\begin{CodeOutput}
# A tibble: 4 x 6
# Groups:   sim [2]
  Type               sim     t     S     I     R
  <chr>            <dbl> <dbl> <dbl> <dbl> <dbl>
1 Simple SIR           1     0   188     0     0
2 Simple SIR           1     1   187     1     0
3 true observation     0    54     1     0   187
4 true observation     0    55     1     0   187
\end{CodeOutput}
\begin{CodeInput}
R> compression_df <- all_together_df %>% group_by(Type, sim) %>% 
+   filament_compression(data_columns = c("S","I","R"), 
+                        number_points = 20)
\end{CodeInput}
\end{CodeChunk}

\begin{CodeChunk}
\begin{CodeInput}
R> dmat <- compression_df %>% 
+   dist_matrix_innersq_direction(
+     position = c(1:length(compression_df))[
+       names(compression_df) %in% c("S","I", "R")],
+     id_as_columns = T)
R> 
R> tdmat <- tidy_dist_mat(as.matrix(dmat[,-c(1:2)]),
+                        rownames_df = ungroup(dmat[,1:2]),
+                        colnames_df = ungroup(dmat[,1:2])) 
R> 
R> 
R> simple_sir_true_obs_info <- tdmat %>% 
+   compare_new_to_rest_via_distance(
+     new_name_id = data.frame(Type = "true observation", sim = 0),
+     distance_func = distance_psuedo_density_function, 
+     sigma = "20%") 
\end{CodeInput}
\end{CodeChunk}

\caption{\label{tab:hags-extreme}The extremeness of the true simulations based on comparing psuedo-density estimates between true vs simulated curves}
\centering
\begin{tabular}[t]{l>{\raggedleft\arraybackslash}p{6cm}>{\raggedleft\arraybackslash}p{6cm}}
\toprule
Type & simulations-based estimated psuedo-density & proportion of simulations with lower estimated psuedo-density\\
\midrule
Simple SIR & 0.0036733 & 0\\
EpiModel SIR & 0.0028813 & 0\\
\bottomrule
\end{tabular}
\end{table}
